### 2023-02-27 intro.tex
Type hole inference future work updated. Pre update to constraint generation rules and narrative

Contemporary programming environments provide 
a wide variety of semantic services that require statically analyzing the type and binding structure of the program being edited, e.g. various semantic navigation services, type hints, semantic code completion, and automated refactoring.

Language designers typically specify static type systems as a collection of rules 
stating conditions under which an expression can be judged to be well-typed,
i.e. completely free of type errors. 
Provisioning these semantic services for well-typed expressions is well-supported 
by these definitions.

>>>>

Contemporary programming environments provide 
a variety of semantic services that require statically analyzing the type and binding structure of the program being edited, e.g. semantic navigation, type hints, semantic code completion, and automated refactoring. However, during the editing process,
it is common for programs to be ill-typed.

Language designers typically specify static type systems as a collection of rules 
stating conditions under which an expression can be judged to be well-typed,
i.e. completely free of type errors. 
 is well-supported 
by these definitions.
